Advances in Artificial Intelligence for Data Visualization: Developing Computer Vision Models to Automate Reading of Data Plots, with Application to Predictive Model Diagnostics

### 2024-08-24 Thesis/abstract.qmd
fill in front matter not sure if it is correct

::: {.content-visible when-format="pdf"}

@@

The inclusion of co-authors reflects the fact that the work came from active collaboration between researchers and acknowledges input into team-based research. In the case of @paper-1 to  @sec-third-paper, my contribution to the work involved the following:

XXX This is Sherry's summary. You need to revise it for your works.

```{r}
#| message: false
#| echo: false
library(tidyverse)
library(knitr)
library(kableExtra)
dt <- tribble(
  ~`Chapter`, ~`Publication title`, ~Status, ~`Student contribution`, ~`Co-authors contribution`, ~`Monash Student Yes/No’`,
  2, "Visual Diagnostics for Constrained Optimisation with Application to Guided Tours", "Published in the R Journal; The R package ferrn on CRAN", "80%  Concept, Analysis, Software, Writing", "D. Cook 10%,  \n P. Menéndez 5%, \n U. Laa 2.5%,  \n N. Langrené 2.5%", "No",
  3, "Cubble: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data", "In revision for the Journal of Statistical Software; The R package cubble on CRAN", "80% Concept, Analysis, Software, Writing", "D. Cook 10%,  \n P. Menéndez 5%, \n U. Laa 2.5%,  \n N. Langrené 2.5%", "No",
)

dt |>
  kable(booktabs = TRUE, format = "latex", longtable = TRUE) |>
  kable_styling(font_size = 10, 
                latex_options = c("hold_position", "repeat_header")) |>
  column_spec(1, width = "1.2cm") |>
  column_spec(2, width = "3cm") |>
  column_spec(3, width = "3.5cm") |>
  column_spec(4, width = "2.5cm") |>
  column_spec(5, width = "2.4cm") |>
  column_spec(6, width = "1.3cm") |>
  row_spec(0, align = "l", bold = TRUE)
```

Chapter 4, *A Tidy Framework and Infrastructure to Systematically Assemble Spatio-temporal Indexes from Multivariate Data* is to be submitted for the Journal of Computational and Graphical Statistics and the associated R package `tidyindex` is to be submitted to CRAN.

**The thesis is written in Australian spelling, except for Chapters 3 and 4, which use American spelling as specified by the publication venue.**

@@

**Student name**: H. Sherry Zhang

@@

**Date**: 23rd August 2023

@@

**Date**: 23rd August 2023

:::

>>>>

@@

The inclusion of co-authors reflects the fact that the work came from active collaboration between researchers and acknowledges input into team-based research. In the case of @sec-first-paper and @sec-third-paper, my contribution to the work involved the following:

```{r}
#| message: false
#| echo: false
library(tidyverse)
library(knitr)
library(kableExtra)
dt <- tribble(
  ~`Chapter`, ~`Publication title`, ~Status, ~`Student contribution`, ~`Co-authors contribution`, ~`Coauthors are Monash students`,
  2, "A Plot is Worth a Thousand Tests: Assessing Residual Diagnostics with the Lineup Protocol", "Published in the Journal of Computational and Graphical Statistics", "80%  Concept, Analysis, Software, Writing", "D. Cook 10%,  \n P. Menéndez 5%, \n U. Laa 2.5%,  \n N. Langrené 2.5%", "No",
  # 3, "Automated Assessment of Residual Plots with Computer Vision Models", "Unsubmitted", "80% Concept, Analysis, Software, Writing", "D. Cook 10%,  \n P. Menéndez 5%, \n U. Laa 2.5%,  \n N. Langrené 2.5%", "No",
  4, "Software for Automated Residual Plot Assessment: autovi and autovi.web", "The R package autovi on CRAN", "80% Concept, Analysis, Software, Writing", "D. Cook 10%,  \n P. Menéndez 5%, \n U. Laa 2.5%,  \n N. Langrené 2.5%", "No"
)

dt |>
  kable(booktabs = TRUE) |>
  kable_styling(font_size = 10,
                latex_options = c("hold_position", "repeat_header")) |>
  column_spec(1, width = "1.2cm") |>
  column_spec(2, width = "3cm") |>
  column_spec(3, width = "3.5cm") |>
  column_spec(4, width = "2.5cm") |>
  column_spec(5, width = "2.4cm") |>
  column_spec(6, width = "1.3cm") |>
  row_spec(0, align = "l", bold = TRUE)
```

Chapter 3, *Automated Assessment of Residual Plots with Computer Vision Models* is to be submitted for the Journal of Computational and Graphical Statistics.

<!-- **The thesis is written in Australian spelling, except for Chapters 3 and 4, which use American spelling as specified by the publication venue.** -->

@@

**Student name**: Weihao Li

@@

**Date**: 26th August 2024

@@

**Date**: 26th August 2024
